---
author: "Harry Churchley"
date: "`r Sys.Date()`"
title: "example: Coca Cola Stock"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{stock-price}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Install dependencies 

```{r}
library(knitr)
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(readr)
library(trendyr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(ggrepel)
```

The data contained in the trendr R package was analyzed exactly like detailed in this document. stockpriceData describes the monthly close price of Coca Cola (KO) between 2010-01-01 and 2020-12-31. 

First, because the data is contained in a package, we can easily call it from R

```{r}
head(stockpriceData)
```
Run trendr on the data and save the output to variable and csv. Three columns are added - observed, trend and first derivative.

```{r}

stockpriceData_trendr <- trendr(df = stockpriceData,
              weekend_effects = FALSE,
              value.colname = "price",
              time.colname = "date",
              output.save = TRUE,
              output.file = "stockpriceData_trendr.csv")

```

Run trendr on the data and plot the results to a graph.

```{r}

trendr(df = stockpriceData,
        weekend_effects = FALSE,
        value.colname = "price",
        time.colname = "date",
        output.plot = TRUE)

```
Plot the data with a connected scatterplot.

```{r}
flightpath(df = stockpriceData_trendr, label_type = 'my')
```











