---
author: "Michael Hodge and Harry Churchley"
date: "`r Sys.Date()`"
title: "example: Japan GDP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{random data}
  %\usepackage[UTF-8]{inputenc}
---

The data contained in the trendr R package was analyzed exactly like detailed in this document. japanGDPData [is a subset of the World Banks Gross Domestic Product (GDP) data set for 1960 to 2018](https://data.worldbank.org/indicator/NY.GDP.MKTP.CD?end=2018&locations=JP)

First, because the data is contained in a package, we can easily call it from R


```{r, include = FALSE}
library(knitr)
knitr::opts_chunk$set(collapse = T, comment = "#>")

library(readr)
library(dplyr)
library(trendyr)

head(japanGDPData)
```

Run trendr on the data and save the results as a variable. Three new columns are added to the data: trend, first_derivative and timeseries.

```{r}
japanGDPData <- japanGDPData %>%
  mutate(year = make_date(year))

head(japanGDPData)

````


```{r}
japanGDPData_trendr <- trendr(df = japanGDPData,
              weekend_effects = FALSE,
              value.colname = "value",
              time.colname = "year",
              #output.save = TRUE,
              output.plot = TRUE)
```

Run trendr on the data and save the results to disk. Three new columns are added to the data: trend, first_derivative and timeseries.

```{r}
trendr::trendr(df = japanGDPData,
        value.colname = 'value',
        time.colname = 'year',
        output.save = TRUE)
```

Run trendr on the data and plot the results to a graph.

```{r}
trendr::trendr(df = japanGDPData,
        value.colname = 'value',
        time.colname = 'year',
        output.plot = TRUE)
```



```{r}

flightpath_copy(df = japanGDPData_trendr, label_type = "y")
```


