---
author: "Michael Hodge and Harry Churchley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteDepends{knitr,readr,dplyr}
  %\VignetteIndexEntry{random data}
  %\usepackage[UTF-8]{inputenc}
---

The data contained in the trendr R package was analyzed exactly like detailed in this document. randomData is a time series of increasing random numbers with a peak.

First, because the data is contained in a package, we can easily call it from R


```{r}
library(knitr)
knitr::opts_chunk$set(collapse = T, comment = "#>")

library(readr)
library(trendyr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(ggrepel)

```

```{r}
head(randomData)
```


Run trendr on the data and save the results as a variable. Three new columns are added to the data: trend, first_derivative and timeseries.

```{r}
output <- trendr(df = randomData,
        value.colname = 'value',
        time.colname = 'date')
output
```

Run trendr on the data and save the results to disk. Three new columns are added to the data: trend, first_derivative and timeseries.

```{r}
trendr(df = randomData,
        value.colname = 'value',
        time.colname = 'date',
        output.save = TRUE)
```

Run trendr on the data and plot the results to a graph.

```{r}
randomData_trendr <- trendr(df = randomData,
        value.colname = 'value',
        time.colname = 'date',
        output.plot = TRUE)
```
Plot the data with a connected scatterplot.

```{r}
flightpath(randomData_trendr)
```