---
author: "Michael Hodge and Harry Churchley"
date: "`r Sys.Date()`"
title: "Example: Random data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteDepends{knitr,readr,dplyr}
  %\VignetteIndexEntry{random data}
  %\usepackage[UTF-8]{inputenc}
---

Install dependencies 

```{r}
library(knitr)
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(readr)
library(trendyr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(ggrepel)
```

The data contained in the trendr R package was analyzed exactly like detailed in this document. randomData is a time series of increasing random numbers with a peak.

First, because the data is contained in a package, we can easily call it from R

```{r}
head(randomData)
```


Run trendr on the data and save the output to a variable and csv. Three columns are added - observed, trend and first derivative.

```{r}
randomData_trendr <- trendr(df = randomData,
              weekend_effects = FALSE,
              value.colname = "value",
              time.colname = "date",
              output.save = TRUE,
              output.file = "randomData_trendr.csv")

head(randomData_trendr)
```
Run trendr on the data and plot the results to a graph.

```{r}
trendr(df = randomData,
        weekend_effects = FALSE,
        value.colname = 'value',
        time.colname = 'date',
        output.plot = TRUE)
```

Plot the data with a connected scatterplot.

```{r}
flightpath(df = randomData_trendr, label_type = 'md')
```
