---
author: "Michael Hodge and Harry Churchley"
date: "`r Sys.Date()`"
title: "Example: Japan GDP"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{random data}
  %\usepackage[UTF-8]{inputenc}
---

Install dependencies 

```{r}
library(knitr)
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(readr)
library(trendyr)
library(dbplyr)
library(lubridate)
library(ggplot2)
library(ggrepel)
```

The data contained in the trendr R package was analyzed exactly like detailed in this document. japanGDPData [is a subset of the World Banks Gross Domestic Product (GDP) data set for 1960 to 2018](https://data.worldbank.org/indicator/NY.GDP.MKTP.CD?end=2018&locations=JP)

First, because the data is contained in a package, we can easily call it from R

```{r}
head(japanGDPData)
```

trendr is designed to take daily data, so we need to convert 'year' to a date.

```{r}
japanGDPData <- japanGDPData %>%
  mutate(year = make_date(year))

head(japanGDPData)

````

Run trendr on the data and save the output to a variable and csv. Three columns are added - observed, trend and first derivative.

```{r}
japanGDPData_trendr <- trendr(df = japanGDPData,
              weekend_effects = FALSE,
              value.colname = "value",
              time.colname = "year",
              output.save = TRUE,
              output.file = "japanGDPData_trendr.csv")

head(japanGDPData_trendr)

```

Run trendr on the data and plot the results to a graph.

```{r}
trendr(df = japanGDPData,
        weekend_effects = FALSE,
        value.colname = "value",
        time.colname = "year",
        output.plot = TRUE)

```

Plot the data with a connected scatterplot.

```{r}

flightpath(df = japanGDPData_trendr, label_type = "y")
```


